Viscous Transport in Eroding Porous Media

### 2019-06-09 docs/transport/erosion_transport.tex
worked on section 4.3

We also do not use any fast summation methods to apply the Barycentric
quadrature rule.  Since this quadrature rule is applied at every GMRES
iteration, it is imperative that we only apply the Barycentric
quadrature at target points where they are required.  As a rule of
thumb, the trapezoid rule due to $\gamma_k$ is accurate if
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if a target point $\xx$
satisfies~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we first check
if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha /geq 1$ is a free parameter that needs to be chosen.
In this manner, we are checking the proximity of the two circles with
centers $\cc_i$ and $\cc_j$, and with radii $L_i$ and $L_j$, where
$\alpha$.  This criteria allows us to quickly determine bodies that
contain discretization points where the Barycentric quadrature rule
should be applied.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
\begin{align}
  \label{eqn:PointsCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \alpha_\iin 
    \left(\frac{L_i}{N_\iin} \right).
\end{align}
By applying this method, we do not have to do an all-to-all comparison
of the discretization points on two eroding bodies.

To determine an appropriate value for $\alpha_\iin$, we first compute an
accurate solution by using the Barycentric quadrature rule for all
discretization points.  Then, for multiple values of $\alpha_\iin$, we
compute the velocity field with the trapezoid rule for all points that
do not satisfy~\eqref{eqn:PointsCutoff}.  By comparing these two
velocities, we find that a value of $\alpha_\iin = ???$ gives sufficient
accuracy while keeping the number of points that require the expensive
Barycentric quadrature rule to a minimum.

Given an eroding body $\gamma_i$, to determine if a target point $\xx$
that is in the fluid bulk rather than on another eroding body requires
the Barycentric quadrature rule, we only check
condition~\eqref{eqn:PointCutoff}.  Finally, to determine if points on
$\gamma_i$ are too close to the outer wall, we make use of the fact that
the outer wall is bounded in $[-3,3] \times [-1,1]$, and that the bodies
are all contained in $[-1,1] \times [-1,1]$.  Therefore, we first check
if
\begin{align}
  \|\cc_i \pm 1\| < L_i + \alpha_\out \frac{L_\out}{N_\out}.
\end{align}
If body $\gamma_i$ satisfies this condition, for each point $\xx \in
\gamma_i$, we apply the Barycentric rule to points that satisfy
\begin{align}
  \|\xx \pm 1\| < \alpha_\out \frac{L_\out}{N_\out}.
\end{align}
Using the same strategy as we used for body-body interactions, we find
that an appropriate safety parameter is $\alpha_\out = ???$.

>>>>

We also do not use any fast summation methods to apply the Barycentric
quadrature rule.  Since this quadrature rule is applied at every GMRES
iteration, it is imperative that we only apply the Barycentric
quadrature at target points where they are required.  As a rule of
thumb, the trapezoid rule due to $\gamma_k$ is accurate if
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target point $\xx$
satisfies~\eqref{eqn:TrapCutoff}, we make use of the {\thL} variables.
First, given the two eroding bodies $\gamma_i$ and $\gamma_j$ with
lengths $L_i$ and $L_j$, and centers $\cc_i$ and $\cc_j$, we first check
if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a free parameter that needs to be chosen.
In this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circles.  This criteria allows us
to quickly determine bodies that contain discretization points where the
Barycentric quadrature rule may need to be applied, and the parameter
$\alpha_\iin$ is accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi} + \alpha_\iin 
    \left(\frac{L_i}{N_\iin} \right).
\end{align}

To determine if points on $\gamma_i$ are too close to the outer wall, we
use the fact that the outer wall is bounded in $[-3,3] \times [-1,1]$,
and that the bodies are all contained in $[-1,1] \times [-1,1]$.
Therefore, we first check if
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      0 \\ \pm 1
    \end{array}
    \right]
  \right\| < L_i + \alpha_\out \frac{L_\out}{N_\out}.
\end{align}
If body $\gamma_i$ satisfies this condition, for each point $\xx \in
\gamma_i$, we apply the Barycentric rule to points that satisfy
\begin{align}
  \label{eqn:PointsWallCutoff}
  \|\xx \pm 1\| < \alpha_\out \frac{L_\out}{N_\out}.
\end{align}

To determine an appropriate value for $\alpha_\iin$ and $\alpha_\out$,
we first compute an accurate solution by using the Barycentric
quadrature rule for all discretization points.  Then, for multiple
values of $\alpha_\iin$ and $\alpha_\out$, we compute the velocity field
with the trapezoid rule for all points that do not satisfy
conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.  By comparing these two velocities, we
find that $\alpha_\iin = ???$ and $\alpha_\out = ???$ give sufficient
accuracy while keeping the number of points that require the expensive
Barycentric quadrature rule to a minimum.

Finally, to determine if a target point $\xx$ that is in the fluid bulk
rather than on another eroding body requires the Barycentric quadrature
rule, we only check conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.
